

The Standard Model of particle physics is a theory of fundamental particles and how they interact. Its the best theoretical framework so far to describe the nature around us. This theory has been experimentally confirmed and all particles predicted by this theory have been found. However, this theory has it shortcomings and can not explain phenomena such as neutrino masses or gravity. The top quark is the heaviest particle in the Standard Model leading and physicists believe that it has an enhanced sensitivity to various new particles and interactions suggested by beyond the Standard Model theories. The top quark has a very short lifetime, so short that it doesn't form bound states and it can be used to study the bare quark. It has distinct signature since it almost exclusively decays to a \PW\ boson and a bottom quark, making it possible to directly study the top quark properties. Many beyond the Standard Model physics phenomena are researched by measuring the production rate of top quarks for studying the $\PW\Ptop\Pbottom$ vertex. Furthermore interactions that are heavily suppressed in the Standard Model can be investigated. The Large Hadron Collider is a top quark factory, producing a large number of events containing top quarks. At the proton collision points, experiments are placed to study the collisions. The search presented in this thesis is performed on data collected by the Compact Muon Solenoid experiment at a centre-of-mass energy of 13 \TeV, resulting in 35.9 \fbinv. 


Flavour changing neutral currents are forbidden at tree level and  highly suppressed at higher order in the Standard Model. However, many beyond the Standard Model theories enhance their probability. In this thesis, a search in three lepton final states is performed for the production of single top quarks via the \tZq\ vertex, with $\Pquark=\Pcharm, \Pup$, or the top quark pair processes where one of the top quarks decay through this vertex.  No significant deviation with respect to the predicted background is observed and upper limits at 95\% confidence level are placed. The observed (expected) upper limits at 95$\%$ confidence level  on the branching fractions are: ${\mathcal{B}}(t \rightarrow uZ) < 0.024\%$ ($0.015\%$) and ${\mathcal{B}}(t \rightarrow cZ) < 0.045\%$ (0.037$\%$), assuming one non-vanishing coupling at a time. 

Significant improvements are developed with respect to previous searches, namely by using other kinematic variables as input into the BDT as well as a better handle on the \NPL\ background.  The expected limit for the FCNC \Zut\ interaction is stronger than the current best observed (expected) limit of 0.017\% (0.024\%) set at a centre-of-mass energy of 13 \TeV\ by ATLAS~\cite{ATLAS-CONF-2017-070}.  The  observed (expected) limit on the \Zct\ interaction set by ATLAS is 0.023\% (0.032\%) and is comparable with the expected limit presented  in this search.  For the FCNC interactions with a \tZq\ vertex, the branching fractions predicted within the Standard Model or beyond the Standard Model theories are still out of reach. 

